\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-09-25 paper/paper.tex
A few more edits and Figure 7 update.

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\section{Background}
\label{sec:Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can break if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout of certain components.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across different components or risks \citep[Chapter 5]{nelson}.  A common assumption in series systems is the time to failure for each risk is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  However, in many situations the cause of failure is unknown to the analyst. This is referred to in the literature as ``masking''.\\

@@

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted Kaplan-Meier estimate with axes on the Weibull probability scale.  Pointwise uncertainty bands associated with each estimator are included. While the Weibull model is inadequate for these data, the GLFP model fits quite well, as it is able to capture the acceleration of the hazard rate between 8000 and 20,000 hours. The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

The set of model specifications were chosen based data, interpretation of the model, as well as estimation considerations.  Product specific parameters for the the wearout failure mode $(\mu_{2g},\sigma_{2g})$, and the proportion defective $(\pi_g)$, are considered as a means to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all product brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the 2nd failure mode to vary by Drive-model.

@@

We can also compare the four Model fits for each Drive-model individually.  For these comparisons, we use the set of parameters which maximize the marginal posterior log probability. Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{b10andpi}
  \caption{Left: 50\% credible intervals for  $t_{0.10}$ (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of $t_{0.10}$.}
  \label{fig4}
\end{figure}

@@

\item[Stan Code] R Stan code for Model 4 (stan file)

@@

\item[Posterior Predictive Graphical Checks for all Drive-Models] Nonparametric estimates of proportion failing for original and replicated data sets for all Drive-models. (pdf file)

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\section{Background}
\label{sec:Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can break if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout of certain components.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across different components or risks \citep[Chapter 5]{nelson}.  A common assumption in series systems is the time to failure for each risk is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  However, in many situations the cause of failure is unknown to the analyst. This is referred to in the literature as masking.\\

@@

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted Kaplan-Meier estimate with axes on the Weibull probability scale.  Pointwise uncertainty bands associated with each estimator are included. While the Weibull model is inadequate for these data, the GLFP model fits quite well, as it is able to capture the acceleration of the hazard rate between 8000 and 20,000 hours. %The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

The set of model specifications were chosen based data, interpretation of the model, as well as estimation considerations.  Product specific parameters for the the wearout failure mode $(\mu_{2g},\sigma_{2g})$, and the proportion defective $(\pi_g)$, are considered as a means to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all product brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the wearout failure mode to vary by Drive-model.

@@

We can also compare the four Model fits for each Drive-model individually.  For these comparisons, we use the posterior median of the MCMC draws. %Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

\begin{figure}[H]
\centering
   \begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{b10new.pdf}
   \caption{50\% CI for $t_{0.10}$}
   \label{fig:Ng1} 
\end{subfigure}

\begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{pinew.pdf}
   \caption{50\% CI for $\pi$}
   \label{fig:Ng2}
\end{subfigure}

\caption{(a) 50\% CI (in years) for $t_{0.10}$ (b) 50\% CI for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of $t_{0.10}$.}
\end{figure}

%\begin{figure}[H]
  %\centering
  %\includegraphics[width=\textwidth]{b10andpi}
  %\caption{Left: 50\% credible intervals for  $t_{0.10}$ (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of $t_{0.10}$.}
  %\label{fig4}
%\end{figure}

@@

\item[Stan Code] Stan code for Model 4 (pdf file)

@@

\item[Posterior Predictive Graphical Checks for all Drive-models] Nonparametric estimates of proportion failing for original and replicated data sets for all Drive-models. (pdf file)
